\title{Timely Reporting of Heavy Hitters using External Memory}

%\author{Anonymous~Submission~to~SIGMOD~2020}

\author{Prashant Pandey}
\authornote{Both authors contributed equally to this research.}
\email{ppandey2@cs.cmu.edu}
\affiliation{\institution{Carnegie Mellon University}
}

\author{Shikha Singh}
\authornotemark[1]
%\authornote{Department of Computer Science, Wellesley College, 106 Central St, Wellesley, MA 02481 USA. Email: \texttt{shikha.singh@wellesley.edu}.}
\email{shikha.singh@wellesley.edu}
\affiliation{%
  \institution{Wellesley College}}

\author{Michael A.~Bender}
%\authornote{Department of Computer Science,
%Stony Brook University, Stony Brook, NY, 11794-2424 USA. Email: \texttt{bender@cs.stonybrook.edu}.}
\email{bender@cs.stonybrook.edu}
\affiliation{%
  \institution{Stony Brook University}}

\author{Jonathan W. Berry}
%\authornote{MS 1326, PO Box 5800, {Albuquerque}, NM, {87185} USA. Email: \texttt{\{jberry, caphill\}@sandia.gov}.}
\email{jberry@sandia.gov}
\affiliation{%
  \institution{Sandia National Laboratories}}
 
\author{Mart\'{\i}n Farach-Colton}
%\authornote{Department of Computer Science, Rutgers University, Piscataway, NJ 08854 USA. Email: \texttt{farach@cs.rutgers.edu}.}
\email{farach@cs.rutgers.edu}
\affiliation{%
  \institution{Rutgers University}}

\author{Rob Johnson}
%\authornote{Creekside F
%3425 Hillview Ave, {Palo Alto}, CA 94304 USA. Email: \texttt{robj@vmware.com}.}
\email{robj@vmware.com}
\affiliation{%
  \institution{VMware Research}}

\author{Thomas M. Kroeger}
%\authornote{MS 9011, PO Box 969, Livermore, CA 94551 USA. Email: \texttt{tmkroeg@sandia.gov}.}
\email{tmkroeg@sandia.gov}
\affiliation{%
  \institution{Sandia National Laboratories}}

\author{Cynthia A. Phillips}
\email{caphill@sandia.gov}
\affiliation{  \institution{Sandia National Laboratories}
}

\renewcommand{\shortauthors}{Pandey and Singh, et al.}

\iffalse
\author{
Michael A.~Bender\thanks{Department of Computer Science, 
Stony Brook University, Stony Brook, NY, 11794-2424 USA. Email:
\texttt{\{bender, ppandey\}@cs.stonybrook.edu}.}
\and
Jonathan W. Berry\thanks{MS 1326, PO Box 5800, {Albuquerque}, NM, {87185} USA. Email: \texttt{\{jberry, caphill\}@sandia.gov}.}
\and 
Mart\'{\i}n Farach-Colton\thanks{Department of Computer Science, Rutgers University, Piscataway, NJ 08854 USA. Email: \texttt{farach@cs.rutgers.edu}.}
\and  
Rob Johnson\thanks{VMware Research, Creekside F
3425 Hillview Ave, {Palo Alto}, CA 94304 USA. Email: \texttt{robj@vmware.com}.}\vspace*{0.2pt}
\and Thomas M. Kroeger\thanks{MS 9011, PO Box 969, Livermore, CA 94551 USA. Email: \texttt{tmkroeg@sandia.gov}.}
\and
Prashant Pandey\footnotemark[1]
\and Cynthia A. Phillips\footnotemark[2]\vspace*{0.2pt} 
\and Shikha Singh\thanks{Department of Computer Science, Wellesley College, Wellesley, MA 02481-8203 USA.  Email: \texttt{shikha.singh@wellesley.edu}.} 
}
\fi
